Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-11-28 paper.tex
Specify homogeneous thermodynamic state in text

\subsection{Infinite Homogeneous Slab:
  Testing Thermodynamic Equilibrium}
\label{ssec:test_equilibrium}
In an optically thick region the radiation field is in thermodynamic equilibrium
with the matter.
We set up a large slab of matter in a Minkowski spacetime
representative of the fluid thermodynamic state at a radius of 50~km
in the test presented in Sec.~\ref{ssec:test_collapse}
(a massive collapsed star following core bounce).
For comparision with that test we use the LS180 equation of state
\cite{latt1991-nuc_eos}
\footnote{available at \lstinline{stellarcollapse.org}}
in which the equilibrium $\nu_e$ neutrino chemical potential is
$\eta_{\nu_e}=-0.1555$
(with $\eta_{\bar{\nu}_e}=-\eta_{\nu_e}$ and $\eta_{\nu_x}=0$).
The opacity table is computed using \lstinline{NuLib} from cross-sections
neglecting weak magnetism
\footnote{TODO: anything else?}
and is stored on a grid covering energy, density, temperature, and composition
ranges spanning $\varepsilon_i\in[1,280.5]$~MeV logarithmically,
$\varrho\in[10^6,6.3\times10^{15}]\,{\rm g}\,{\rm cm}^{-3}$ logarithmically,
$T\in[0.05,200]$~MeV logarithmically, and 
$Y_e\in[0.035,0.55]$ linearly,
with grid extents$\{18,82,65,51\}$ respectively.
Interpolation is performed linearly.

>>>>

\subsection{Infinite Homogeneous Slab:
  Testing Thermodynamic Equilibrium}
\label{ssec:test_equilibrium}
In an optically thick region the radiation field is in thermodynamic equilibrium
with the matter.
We set up a large slab of matter in a Minkowski spacetime
representative of the fluid thermodynamic state at a radius of 50~km
in the test presented in Sec.~\ref{ssec:test_collapse}---a
massive collapsed star following core bounce---where
$\varrho=10^{11}\,{\rm g}\,{\rm cm}^{-3}$, $T=3.7$~MeV, and $Y_e=0.12$.
For comparision with that test we use the LS180 equation of state
\cite{latt1991-nuc_eos}
\footnote{available at \lstinline{stellarcollapse.org}}
in which the equilibrium $\nu_e$ neutrino chemical potential is
$\eta_{\nu_e}=-0.1555$
(with $\eta_{\bar{\nu}_e}=-\eta_{\nu_e}$ and $\eta_{\nu_x}=0$).
The opacity table is computed using \lstinline{NuLib} from cross-sections
neglecting weak magnetism
\footnote{TODO: anything else?}
and is stored on a grid covering energy, density, temperature, and composition
ranges spanning $\varepsilon_i\in[1,280.5]$~MeV logarithmically,
$\varrho\in[10^6,6.3\times10^{15}]\,{\rm g}\,{\rm cm}^{-3}$ logarithmically,
$T\in[0.05,200]$~MeV logarithmically, and 
$Y_e\in[0.035,0.55]$ linearly,
with grid extents$\{18,82,65,51\}$ respectively.
Interpolation is performed linearly.
